Sustainable computational science:\\ the ReScience initiative

### 2017-07-11 draft.tex
abstract, small changes

\twocolumn[
  \maketitle
  \vspace{5mm}
  \noindent
  \textbf{Abstract.}
  If computer science offers a large set of tools for prototyping, writing,
  running, testing, validating, sharing and replicating results, computational
  science still lags behind. In the best case, authors may provide the sources
  of their research as a compressed archive and feel confident their research
  is replicable. But this is not exactly true. Buckheit \& Donoho 1995
  explained almost 20 years ago that, an article about computational result is
  advertising, not scholarship. The actual scholarship is the full software
  environment, code and data that produced the result. The computational part
  in computational sciences implies the use of computers, operating systems,
  tools, frameworks, libraries and data. This leads to such a large number of
  combinations (taking into account the version for each component) that the
  chances to have the exact same configuration as one of your colleagues are
  nearly zero. This draws consequences in our respective computational
  approaches in order to make sure that computational research can be actually
  and faithfully replicated.
  %
  ReScience is a peer-reviewed journal that targets computational research and
  encourages the explicit replication of already published research, promoting
  new and open-source implementations in order to ensure that the original
  research is reproducible. To achieve this goal, the whole publishing chain is
  radically different from other traditional scientific journals. ReScience
  lives on GitHub where each new implementation of a computational study is
  made available together with comments, explanations and tests. Each
  submission takes the form of a pull request that is publicly reviewed and
  tested in order to guarantee that any researcher can re-use it. ReScience is
  open and collaborative by design: everything can be modified.\\
  % \begin{small}
  % \vspace{10mm}

>>>>

\twocolumn[
  \maketitle
  \vspace{5mm}
  \noindent
  \textbf{Abstract.}
  Computer science offers a large set of tools for prototyping, writing,
  running, testing, validating, sharing and replicating results, however computational
  science lags behind.
  In the best case, authors may provide their source code as a compressed archive and they may feel confident their research
  is replicable. But this is not exactly true. Buckheit \& Donoho 1995
  proposed more than 2 decades ago that, an article about computational results is
  advertising, not scholarship. The actual scholarship is the full software
  environment, code, and data that produced the result. The computational part
  in computational sciences implies the use of computers, operating systems,
  tools, frameworks, libraries, and data. This leads to a large number of
  combinations thereof (taking into account the version for each component) that the
  chances of having the exact same configuration as one of your colleagues are
  practically zero. This has consequences for computational
  approaches in order to make sure that computational research can be faithfully replicated.
  %
  ReScience is a peer-reviewed journal that targets computational research and
  encourages the explicit replication of already published research, promoting
  new and open-source implementations in order to ensure that the original
  research is reproducible. To achieve this goal, the whole publishing chain is
  radically different from other traditional scientific journals. ReScience
  resides on GitHub where each new implementation of a computational study is
  made available together with comments, explanations, and software tests. Each
  submission takes the form of a ``pull request'' that is publicly reviewed and
  tested in order to guarantee re-usability. ReScience is
  open and collaborative by design: everything can be modified.\\
  % \begin{small}
  % \vspace{10mm}
